### 2015-01-19 src/methodology.Rnw
cleanup with xspace

% Figure~\ref{fig:op} shows
% the distribution of mutants and the relative detection rates of each
% mutation operator for our projects. In the figure, there are two box-plots
% corresponding to each mutation operator on the Y-axis. The black box represents
% the relative frequency of the particular mutation operator in the total
% mutants \textit{produced}. For example, for projects in the (Randoop) generated set,
% the operator \pitnvmc contributed about 34\% of the total number of mutants
% produced while \pitrv contributed about 7\%. Similarly, the blue shaded
% box-plot represents the relative frequency of particular mutation operator
% in the total mutants \textit{detected}. For example, \pitnvmc contribution
% in the detected mutants was 23\% while that of \pitrv was 15\%.

@@

\begin{table}
\small{
\begin{tabular}{ll}
\hline \hline \\
\pitin & Remove negative sign from numbers\\
\pitrv & Mutate return values\\
\pitm & Mutate arithmetic operators\\
\pitvmc & Remove void method calls\\
\pitnc & Negate conditional statements\\
\pitcb & Modify boundaries in logical conditions\\
\piti & Modify increment and decrement statements\\
\pitnvmc & Remove non-void method calls, returning default value \\
\pitcc & Replace constructor calls, returning null \\
\pitic & Replace inline constants with default value \\
\pitri & Remove increment and decrement statements \\
\pitemv & Replace member variable assignments with default value \\
\pites & Modify switch statements \\
\pitrs & Replace switch labels with default (thus removing them) \\
\pitrc & Replace boolean conditions with true\\
\pitnc & Replace boolean conditions with false\\
\hline
\end{tabular}
}
\caption{PIT Mutation Operators (We have used abbreviations instead of operator names.)}
\label{tbl:pitop}
\end{table}

@@

\subsubsection{Constrained Mutation}
\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.}
They selected ROR  and ABS  from Mothra for
mutation analysis. We used operators
\pitcb and \pitnc to model ROR operator. There are no comparable operators to ABS in PIT.

@@

The statement deletion based operator selection was based on the work by
Deng et al.~\cite{deng2013empirical}. The operations on single
statements were modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and
\Pitri~for simple statements, and using \pitrc for control structures. \pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.

@@

% Finally, to get an accurate estimation
% of the effect of true statement deletion, we grouped the mutants by
% line, and considered each line a single virtual mutant (that is, the total
% number of mutants is equal to the total number of lines). Further,
% killing any mutant from a line resulted in marking the virtual mutant
% for that line as killed. This gave us the mutation score for the
% virtual statement deletion operator.  We note that the approximation
% of simple statement deletion, especially when arithmetic operators are
% involved, is not complete. However,
% the number of mutants produced by \pitm operator is very small. We
% also note that our approximation does not account for the increase in
% ease of detection when multiple mutations are combined together due to
% the coupling effect. This also means that not all the lines may be
% mutated ,since there may be no applicable operators. However, given
% the constraints of a bytecode based mutation system, we believe that
% our procedure is reasonable.
% An interesting point is that using this

>>>>

% Figure~\ref{fig:op} shows
% the distribution of mutants and the relative detection rates of each
% mutation operator for our projects. In the figure, there are two box-plots
% corresponding to each mutation operator on the Y-axis. The black box represents
% the relative frequency of the particular mutation operator in the total
% mutants \textit{produced}. For example, for projects in the (Randoop) generated set,
% the operator \pitnvmc contributed about 34\% of the total number of mutants
% produced while \pitrv contributed about 7\%. Similarly, the blue shaded
% box-plot represents the relative frequency of particular mutation operator
% in the total mutants \textit{detected}. For example, \Pitnvmc contribution
% in the detected mutants was 23\% while that of \Pitrv was 15\%.

@@

\begin{table}
\small{
\begin{tabular}{ll}
\hline \hline \\
\Pitin & Remove negative sign from numbers\\
\Pitrv & Mutate return values\\
\Pitm & Mutate arithmetic operators\\
\Pitvmc & Remove void method calls\\
\Pitnc & Negate conditional statements\\
\Pitcb & Modify boundaries in logical conditions\\
\Piti & Modify increment and decrement statements\\
\Pitnvmc & Remove non-void method calls, returning default value \\
\Pitcc & Replace constructor calls, returning null \\
\Pitic & Replace inline constants with default value \\
\Pitri & Remove increment and decrement statements \\
\Pitemv & Replace member variable assignments with default value \\
\Pites & Modify switch statements \\
\Pitrs & Replace switch labels with default (thus removing them) \\
\Pitrc & Replace boolean conditions with true\\
\Pitnc & Replace boolean conditions with false\\
\hline
\end{tabular}
}
\caption{PIT Mutation Operators (We have used abbreviations instead of operator names.)}
\label{tbl:pitop}
\end{table}

@@

\subsubsection{Constrained Mutation}
\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.}
They selected ROR  and ABS  from Mothra for
mutation analysis. We used operators
\Pitcb and \Pitnc to model ROR operator. There are no comparable operators to ABS in PIT.

@@

The statement deletion based operator selection was based on the work by
Deng et al.~\cite{deng2013empirical}. The operations on single
statements were modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and
\Pitri~for simple statements, and using \Pitrc for control structures. \Pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \Pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.

@@

% Finally, to get an accurate estimation
% of the effect of true statement deletion, we grouped the mutants by
% line, and considered each line a single virtual mutant (that is, the total
% number of mutants is equal to the total number of lines). Further,
% killing any mutant from a line resulted in marking the virtual mutant
% for that line as killed. This gave us the mutation score for the
% virtual statement deletion operator.  We note that the approximation
% of simple statement deletion, especially when arithmetic operators are
% involved, is not complete. However,
% the number of mutants produced by \Pitm operator is very small. We
% also note that our approximation does not account for the increase in
% ease of detection when multiple mutations are combined together due to
% the coupling effect. This also means that not all the lines may be
% mutated ,since there may be no applicable operators. However, given
% the constraints of a bytecode based mutation system, we believe that
% our procedure is reasonable.
% An interesting point is that using this

### 2015-01-19 src/paper.Rnw
cleanup with xspace

% MAX LIMIT: 10 pages for all figurs and text + any number of references.
\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
%\newcommand{\pitnvmc}{~NON\_\allowbreak{}VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
%\newcommand{\pitnc}{~NEGATE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitrc}{~REMOVE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitdc}{~DELETE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitrv}{~RETURN\_\allowbreak{}VALUES~}
%\newcommand{\pitic}{~INLINE\_\allowbreak{}CONSTANTS~}
%\newcommand{\pitcc}{~CONSTRUCTOR\_\allowbreak{}CALLS~}
%\newcommand{\pitemv}{~E\_\allowbreak{}MEMBER\_\allowbreak{}VARIABLE~}
%\newcommand{\pitvmc}{~VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
%\newcommand{\pitm}{~MATH~}
%\newcommand{\pitcb}{~CONDITIONALS\_\allowbreak{}BOUNDARY~}
%\newcommand{\piti}{~INCREMENTS~}
%\newcommand{\pitri}{~REMOVE\_\allowbreak{}INCREMENTS~}
%\newcommand{\pitrs}{~RM\_\allowbreak{}SWITCH~}
%\newcommand{\pites}{~E\_\allowbreak{}SWITCH~}
%\newcommand{\pitin}{~INVERT\_\allowbreak{}NEGATIVES~}
%
\newcommand{\pitnvmc}{NMC~}
\newcommand{\pitnc}{NC~}
\newcommand{\pitrc}{RC~}
\newcommand{\pitdc}{DC~}
\newcommand{\pitrv}{RV~}
\newcommand{\pitic}{IC~}
\newcommand{\pitcc}{CC~}
\newcommand{\pitemv}{EMV~}
\newcommand{\pitvmc}{VMC~}
\newcommand{\pitm}{M~}
\newcommand{\pitcb}{CB~}
\newcommand{\piti}{I~}
\newcommand{\pitri}{RI~}
\newcommand{\pitrs}{RS~}
\newcommand{\pites}{ES~}
\newcommand{\pitin}{IN~}
% No space variants.
\newcommand{\Pitnvmc}{NMC}
\newcommand{\Pitnc}{NC}
\newcommand{\Pitrc}{RC}
\newcommand{\Pitdc}{DC}
\newcommand{\Pitrv}{RV}
\newcommand{\Pitic}{IC}
\newcommand{\Pitcc}{CC}
\newcommand{\Pitemv}{EMV}
\newcommand{\Pitvmc}{VMC}
\newcommand{\Pitm}{M}
\newcommand{\Pitcb}{CB}
\newcommand{\Piti}{I}
\newcommand{\Pitri}{RI}
\newcommand{\Pitrs}{RS}
\newcommand{\Pites}{ES}
\newcommand{\Pitin}{IN}

\begin{comment}
<<setup, include=FALSE, message=FALSE, echo=FALSE>>=
is.installed <- function(mypkg) is.element(mypkg, installed.packages()[,1])
#options(CRAN = "http://cran.stat.ucla.edu")
#if (!is.installed("xtable")) install.packages("xtable")
#if (!is.installed("ggplot2")) install.packages("ggplot2")
#if (!is.installed("reshape2")) install.packages("reshape2")

#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(scales)
require(xtable)
require(ggplot2)
require(MutSel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='MutSel')
data(list = v$results[,3])
@
\end{comment}
<<>>=

f <- function(x) {
  x <- x[,c(7,8,2,3,4,5,6)]
  names(x)[names(x) == 'sampling'] <- '$\\div$'
  return(x)
}

colorize.rsqr <- function(x) {
  ifelse(x >= 0.90,
      paste("\\textcolor{blue}{", formatC(x, dig=2, format="f"), "}"),
      paste("\\textcolor{black}{", formatC(x, dig=2, format="f"), "}"))
}

colorize.it <- function(x) {
  x$sd.reduction <- ifelse(x$sd.reduction * 2 < x$mutant.reduction,
      paste("\\textcolor{black}{", formatC(x$sd.reduction, dig=2, format="f"), "}"),
      paste("\\textcolor{red}{", formatC(x$sd.reduction, dig=2, format="f"), "}"))
  x$r.square <- colorize.rsqr(x$r.square)
  return(x)
}

theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())

@
% 10 pages for the main text + 1 for references.
<<introduction, child='introduction.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@

>>>>

% MAX LIMIT: 10 pages for all figurs and text + any number of references.
\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis\xspace}
\newcommand\mua{mutation analysis\xspace}
\newcommand{\Pitnvmc}{NMC\xspace}
\newcommand{\Pitnc}{NC\xspace}
\newcommand{\Pitrc}{RC\xspace}
\newcommand{\Pitdc}{DC\xspace}
\newcommand{\Pitrv}{RV\xspace}
\newcommand{\Pitic}{IC\xspace}
\newcommand{\Pitcc}{CC\xspace}
\newcommand{\Pitemv}{EMV\xspace}
\newcommand{\Pitvmc}{VMC\xspace}
\newcommand{\Pitm}{M\xspace}
\newcommand{\Pitcb}{CB\xspace}
\newcommand{\Piti}{I\xspace}
\newcommand{\Pitri}{RI\xspace}
\newcommand{\Pitrs}{RS\xspace}
\newcommand{\Pites}{ES\xspace}
\newcommand{\Pitin}{IN\xspace}

<<rsetup, child='r.setup.Rnw'>>=
@
% 10 pages for the main text + 1 for references.
<<introduction, child='introduction.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
